---
title: "ESM206_Lab10"
author: "Kirsten White"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(usethis)

library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)

```

## beepr::beep()

Use `beep()` to give yourself an audio alert

## for loop + beep()

```{r, eval = FALSE}
for (i in rev(seq(1:999))) {
  print(paste(i, "bottles of beer on the wall"))}
beep(6)
```
## praise is nice - prints out random nice messages
"${gramatical piece that R recognizes} see ?praise in console 

```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${creating}, Batman - this code works ${adverb_manner}!")
```

## cowsay::say to have characters say something 
see ?say in console for other arguments (characters , etc) 

Open to Rprofile: add --> cowsay::say(praise::praise("You are ${ADJECTIVE}!"), by = "pumpkin")
```{r}
say("I love tacos!", by = "pumpkin")

```

## usethis for everything 

R project first, then git & GitHub repo

- usethis::use_git() 
- usethis::use_github() 

## use paletteer: aggregated color palettes 

- in console, type: view(palettes_d_names) to see palettes

```{r}
storms %>%
  group_by(name) %>%
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>%
  slice_min(n = 10, min_pressure) %>% # find storms with lowest minimum pressure 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d()
```


